Supplementary material to: Drug efficacy prediction in cell lines

### 2019-01-02 docs/supplement.Rnw
second simulation run finished

>>>>

<<"boxplot_igaussian_res2_theta", fig.cap="a) MSE and b) correlation for prior means of $\\gamma_d^2$ ($\\theta_d$) in simulation 2", fig.align="center", echo=FALSE>>=
res2 <- read.table("../results/simulations_igaussian_res2.csv")
set2 <- read.table("../results/simulations_igaussian_set2.csv")
names1 <- c("inv Gauss", "ind inv Gauss", "inv Gamma")
temp1 <- list(res2[, substr(colnames(res2), 1, 15)=="theta.inv.Gauss"],
              res2[, substr(colnames(res2), 1, 19)=="theta.ind.inv.Gauss"],
              res2[, substr(colnames(res2), 1, 16)=="aprior.inv.Gamma"],
              res2[, substr(colnames(res2), 1, 16)=="bprior.inv.Gamma"])
temp2 <- list(colMeans((t(temp1[[1]]) - 
                          as.numeric(set2[, substr(colnames(set2), 1, 5)=="theta"]))^2),
              colMeans((t(temp1[[2]]) - 
                          as.numeric(set2[, substr(colnames(set2), 1, 5)=="theta"]))^2),
              colMeans((t(temp1[[4]]/(temp1[[3]] - 1)) - 
                          unique(as.numeric(set2[, substr(colnames(set2), 1, 5)=="theta"])))^2))
temp3 <- list(apply(t(temp1[[1]]), 2, function(r) {
  cor(r, as.numeric(set2[, substr(colnames(set2), 1, 5)=="theta"]))}),
              apply(t(temp1[[2]]), 2, function(r) {
                cor(r, as.numeric(set2[, substr(colnames(set2), 1, 5)=="theta"]))}),
              apply(t(temp1[[4]]/(temp1[[3]] - 1)), 2, function(r) {
                cor(r, unique(as.numeric(set2[, substr(colnames(set2), 1, 5)=="theta"])))}))
par(cex=1.3)
layout(matrix(c(rep(1, 4), rep(2, 4)), 2, 4), widths=1, heights=1, respect=TRUE)
boxplot(temp2, names=names1, ylab="MSE", main="a)")
legend("bottomright", title=expression(bold("median MSE")), bty="n",
       paste(names1, round(sapply(temp2, median), 2), sep="="))
boxplot(temp3, names=names1, ylab="Correlation", main="b)")
legend("bottomleft", title=expression(bold("median correlation")), bty="n",
       paste(names1, round(sapply(temp3, median), 2), sep="="))
par(cex=1)
layout(matrix(1, 1, 1), widths=1, heights=1, respect=TRUE)
@

<<"boxplot_igaussian_res1_alpha", fig.cap="a) MSE and b) correlation for $\\alpha$", fig.align="center", echo=FALSE>>=
res2 <- read.table("../results/simulations_igaussian_res2.csv")
set2 <- read.table("../results/simulations_igaussian_set2.csv")

names1 <- c("inv Gauss", "ind inv Gauss")
temp1 <- list(res2[, substr(colnames(res2), 1, 15)=="alpha.inv.Gauss"],
              res2[, substr(colnames(res2), 1, 19)=="alpha.ind.inv.Gauss"])
temp2 <- list(colMeans((t(temp1[[1]]) - as.numeric(set2[, substr(colnames(set2), 1, 5)=="alpha"]))^2),
              colMeans((t(temp1[[2]]) - as.numeric(set2[, substr(colnames(set2), 1, 5)=="alpha"]))^2))
temp3 <- list(apply(t(temp1[[1]]), 2, function(r) {cor(r, as.numeric(set2[, substr(colnames(set2), 1, 5)=="alpha"]))}),
              apply(t(temp1[[2]]), 2, function(r) {cor(r, as.numeric(set2[, substr(colnames(set2), 1, 5)=="alpha"]))}))
par(cex=1.3)
layout(matrix(c(rep(1, 4), rep(2, 4)), 2, 4), widths=1, heights=1, respect=TRUE)
boxplot(temp2, names=names1, ylab="MSE", main="a)")
legend("topright", title=expression(bold("median MSE")), bty="n",
       paste(names1, round(sapply(temp2, median), 2), sep="="))
boxplot(temp3, names=names1, ylab="Correlation", main="b)")
legend("bottomright", title=expression(bold("median correlation")), bty="n",
       paste(names1, round(sapply(temp3, median), 2), sep="="))
par(cex=1)
layout(matrix(1, 1, 1), widths=1, heights=1, respect=TRUE)
@

<<>>=
fit2 <- read.table("../results/simulations_igaussian_fit2.csv")
plot(fit2[, substr(colnames(fit2), 1, 15)=="inv.Gauss.alpha"][, 1], type="l",
     ylim=range(fit2[, substr(colnames(fit2), 1, 15)=="inv.Gauss.alpha"]))
for(i in 2:5) {
  lines(fit2[, substr(colnames(fit2), 1, 15)=="inv.Gauss.alpha"][, 2], col=i)  
}
@
